\begin{center}
    {\Huge \scshape Kinshuk Phalke} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ (404)-519-7018 ~ \href{mailto:phalkekinshuk@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{phalkekinshuk@gmail.com}} ~ 
    \href{https://linkedin.com/in/kinshukphalke/}{\raisebox{-0.2\height}\faLinkedin\ \underline{kinshukphalke}}  ~
    \href{https://github.com/xinslu}{\raisebox{-0.2\height}\faGithub\ \underline{xinslu}} ~
    \href{https://kinshukphalke.com/}{\raisebox{-0.2\height}\faLink\ \underline{kinshukphalke.com}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{August 2024 - December 2025}
      {Masters of Science in Computer Science, Specialization in Machine Learning}{Atlanta, Georgia}
  \resumeSubHeadingListEnd
\vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{August 2021 - May 2024}
      {Bachelor of Science in Computer Science, GPA: 4.0}{Atlanta, Georgia}
    \resumeItemListStart
    \resumeItem{\textbf{Concentration: } System and Architecture, Intelligence}
    \resumeItem{\textbf{Clubs: } President dependently-typed (Programming Languages Club)}
    \resumeItem{\textbf{Awards: } GT Intern Student of the Year 2024}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

  \vspace{-16pt}

%-----------EXPERIENCE-----------

\section{Experience}

  \resumeSubHeadingListStart

    \resumeSubheading
      {Meta}{May 2025 -- August 2025}
      {Software Engineering Intern}{Menlo Park, California}
      \resumeItemListStart
        \resumeItem{Designed and launched a new feature enabling users to replace reel audio with copyright-free tracks, driving ad creation.}
        \resumeItem{Built a video and audio editor with real-time preview and audio track selection streamlining content editing.}
        \resumeItem{Developed end-to-end test suites and led engagement experiments to assess interactions on new experience.}
      \resumeItemListEnd

    \resumeSubheading
      {NCR Voyix}{May 2024 -- August 2024}
      {Software Engineering Intern}{Atlanta, Georgia}
      \resumeItemListStart
        \resumeItem{Designed a deployable Electron.js testing bench that allows testing on different conditions without physical hardware.}
        \resumeItem{Integrated with deployed VNC and XServer services allowing headed end-to-end tests to run on production.}
        \resumeItem{Automated deployment and testing via Feature Flag leading to reduction in time required for testing and setup by 10x.}
      \resumeItemListEnd

    \resumeSubheading
      {NCR Corporation}{May 2023 -- August 2023}
      {Software Engineering Intern Team Lead}{Atlanta, Georgia}
      \resumeItemListStart
        \resumeItem{Lead a team of 5 interns in designing an end-to-end organization generation micro-service in Python, for SIT testing.}
        \resumeItem{Designed core logic in catalog generation from dataset, store location randomization and organization provisioning.}
        \resumeItem{Trained a NER model to recognize brands from products and a transformer model to generate product descriptions.}
        \resumeItem{Deployed API on Google Kubernetes Engine and designed a CI/CD pipeline to test and publish cluster.}
      \resumeItemListEnd

    \resumeSubheading
      {Georgia Tech High Performance Architecture Lab}{Jan 2023 -- May 2024}
      {Undergraduate Research Assistant}{Atlanta, Georgia}
      \resumeItemListStart
        \resumeItem{Devloping hybrid SSD-GPU architectures and scheduling strategies to maximize bandwidth and performance in GPUs.}
        \resumeItem{Developed an SSD Scheduling Algorithm that led to around a percentage increase in throughput and IOPS in comparision with exisisting algorithms.}
        \resumeItem{Published Thesis: \textit{Maximizing SSD Bandwidth Efficiency Through In-Storage GPU Integration}.}
      \resumeItemListEnd

    \resumeSubheading
      {NCR Corporation}{May 2022 -- August 2022}
      {Software Engineer Intern}{Atlanta, Georgia}
      \resumeItemListStart
        \resumeItem{Developed a shopping cart micro service in Go Fiber deployed onto GCP to enable carting on PoS devices and websites.}
        \resumeItem{Designed core logic in CRUD operations of cart and service integration into NCR's BSP layer for related taxes, prices, store locations, promotions, returns and item attributes information and operations.}
        \resumeItem{Architected a CI/CD pipeline to run testing suite, verify and publish deployments, publish artifacts onto GCP.}
        \resumeItem{Automated management of environment in production, Kubernetes cluster, pods, deployment and CA certificates.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Notitia}{November 2021 -- December 2022}
    %   {Software Engineer}{Atlanta, Georgia}
    %   \resumeItemListStart
    %     \resumeItem{Built a LDA model in Python for Topic Discovery capabale of ingesting 50K tokens, tuned UMAP parameters to achieve a 80\% accuracy in dimensionality reduction, utilized FAISS in clustering, designed WordCloud UI using React Flow.}
    %     \resumeItem{Optimized the frontend graph rendering by 60\% and backend machine learning algorithm by 40\%.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-2pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading{\textbf{DeusCL}}{Rust, Common Lisp, Yew Framework}
          \resumeItemListStart
            \resumeItem{Developed a memory-safe REPL in Rust using a handwritten recursive descent parser and a visitor pattern evaluator.}
            \resumeItem{Implemented basic type inference, type checking, error handling system, lexically scoped garbage collector and a dynamic evaluation of functional environment and parameters. }
            \resumeItem{Designed a frontend in Yew Framework in Rust to enable users to use a web based simulation of REPL.}
          \resumeItemListEnd

      % \resumeProjectHeading{\textbf{SpeechToCode}}{Python, ReactJS, Node.js}
      %     \resumeItemListStart
      %       \resumeItem{Developed meta language parser in Python to create functional JavaScript, Python or Java code from spoken english.}
      %       \resumeItem{Implemented a visitor pattern, lexical scoping system, text based type inference system to create language output.}
      %       \resumeItem{Integrated with the speech to text machine learning flask server and designing the frontend in ReactJS.}
      %     \resumeItemListEnd


      \resumeProjectHeading{\textbf{Publixmon}}{MongoDB, Express.JS, React Native, Node.JS, Flask, Node.js}
          \resumeItemListStart
            \resumeItem{Developed a Web3 mobile app in React Native allowing users to play NFT trading game to boost retail engagement.}
            \resumeItem{Integrated with the NCR BSP layer for order, catalog, inventory details and generate an NFT based on user history.}
            \resumeItem{Tested mining NFTs on the Ganache Blockchain via a node.js server to facilitate Smart Contracts from the App.}
            \resumeItem{Project won the first place at the NCR API Challenge at HackGT 8.}
          \resumeItemListEnd 

      % \resumeProjectHeading
      %     {\textbf{Enhance}}{Python, Tensorflow, Keras}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Res-Net Implementation of the Super Resolution GAN Paper for Super Resolution in Tensorflow.}
      %       \resumeItem{Implemented residual blocks and skip connection, Used the VGG-19 model to calculate the content loss of the model. }
      %       \resumeItem{Achieved perceptible improvements in image quality on the DIV2K dataset with a downscale factor 4.}
      %     \resumeItemListEnd 

    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in,label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Go, Rust, C, TypeScript, JavaScript, Java, C\#} \\
     \textbf{Frameworks}{: ReactJS, Next.JS, Astro, Node.js, Express.js, React Native} \\
     \textbf{Machine Learning}{: Tensorflow, PyTorch, NumPy, Scikit-learn, Matplotlib, Pandas, Keras, NLTK} \\
     \textbf{Technologies}{: Git, Linux, Docker, Postman, \LaTeX, MongoDB, Redis, Kubernetes, GCP, AWS, Web3} \\
    }}
 \end{itemize}
 \vspace{-16pt}
